Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-12-16 R0V0.tex
Item 12
Item 13

\mypara A suitable notion to deal with exponential convergence of pair of solutions to \eqref{eq:general system} is provided by the \emph{differential} (also known as variational or prolonged) dynamical system
\begin{equation}\label{eq:general system:differential}
	\dot{\delta}_x=A(x,u)\delta_x+B(x)\delta_u\;,
\end{equation}
where $\delta_x$ (resp. $\delta_u$) is a vector of the Euclidean space $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). More precisely, it is the vector tangent to a piecewise smooth curve connecting a pair of points in $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). The matrix $A\in\mathbb{R}^{n\times n}$ has components given, for every $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, by 
\begin{equation*}
	A_{jk}(x,u)=\dfrac{\partial[f_j+b_ju_j]}{\partial x_k}(x,u)	
\end{equation*}
for indexes $j,k\in\mathbb{N}_{[1,n]}$.

@@

\mypara The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows. Given fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively. If the norm of every solution $\Delta_x(t,x,\delta_x,u,\delta_u)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially. The interested reader may address \cite{Lohmiller1998,Sontag2010} and references therein for further details.

>>>>

\mypara A suitable notion to deal with exponential convergence of pair of solutions to \eqref{eq:general system} is provided by the \emph{differential} (also known as variational or prolonged) dynamical system
\begin{equation}\label{eq:general system:differential}
	\dot{\delta}_x=A(x,u)\delta_x+B(x)\delta_u\;,
\end{equation}
where $\delta_x$ (resp. $\delta_u$) is a vector of the Euclidean space $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). More precisely, it is the vector tangent to a piecewise smooth curve connecting a pair of points in $\mathbb{R}^n$ (resp. $\mathbb{R}^m$). The matrix $A\in\mathbb{R}^{n\times n}$ has components given by 
\begin{equation*}
	A_{jk}(x,u)=\dfrac{\partial}{\partial x_k}\left[f_j+\sum_{i=1}^{m_j} B_{ji}u_i\right]
\end{equation*}
for indexes $j,k\in\mathbb{N}_{[1,n]}$.

@@

\mypara The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows. Given a fixed two control $u$ for system \eqref{eq:general system}, $\delta_u\equiv0$. If the Euclidean norm of every solution $\Delta_x(t,x,\delta_x,u,0)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially. The interested reader may address \cite{Lohmiller1998,Sontag2010} and references therein for further details.
